
\begin{acknowledgements}

  I sincerely thank my friends, family and colleagues, whose support throughout
  my PhD candidature played a significant part in the completion of this thesis.

  I am enormously grateful to Associate Professor David Grayden for his primary
  supervision of my doctoral research. Mine was a long and winding candidature,
  and David's clarity, patience and generosity went above and beyond what I
  could ever have expected. 

  Thank you also to my co-supervisors Professor Tony Burkitt and Dr Hamish
  Meffin for their long-standing commitment to and support for my research. I
  had a tremendous supervision team and I feel very lucky to have worked with
  them.

  I wish to thank the staff and students at the research centres I was connected
  to during my candidature: the Centre for NeuroEngineering and the Department
  of Otolaryngology (Royal Victorian Eye and Ear Hospital) at the University of
  Melbourne, and the Bionics Institute (in the days when it was known as the
  Bionic Ear Institute in East Melbourne). I am very fortunate to have been part
  of such a vibrant and diverse community of researchers during my
  candidature. I would particularly like to thank Dr David Sly for his kindness
  and encouragement.

  During my candidature I benefitted from an internship at the Victorian Life
  Sciences Computing Initiative and the IBM Collaboratory, and I thank the staff
  at these institutions for their contribution to my development as a
  researcher. In the closing stages of my candidature I enjoyed the support and
  understanding of my colleagues at Monash Biomedical Imaging, which helped me
  get over the line.

  I have had the unwavering support of my loyal and loving parents Barry and
  Winnie, for which I will always be grateful. I am lucky to be part of a large
  and wonderful family who have taken an interest in what I do and helped me to
  develop my skills in science communication. Thank you Jenny, Mitchell,
  Elizabeth, Stephen, Dee, Emma, Brodie, Leah, Suzanne, Christophe and
  Camille. Thank you also to Stephanie, Alison and Gordon Grant for their
  support and for the thesis-writing time we had in Sandy Bay.

  Finally, thank you to my partner Genevieve. Gentle and supportive in my
  darkest days. Caring and strong after my head injury. Stern and unyielding in
  the home straight of thesis writing. There is no one in the world I would
  rather have in my corner than you. I love you. A lot.

\end{acknowledgements}
